Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-07-14 draftfinalreport_v4.Rnw
add block to compute numbers for text

@@

<<echo=FALSE,include=FALSE,results=hide>>=
rm(list=ls())
#library(adehabitat)
library(classInt)
library(ggplot2)   # plotting library
library(grid)
library(gridExtra)
library(ggmap)
library(Hmisc)
library(maps)       # Provides functions that let us plot the maps
library(mapdata)    # Contains the hi-resolution points that mark out the countries.
library(maptools)
library(mapproj)
library(plyr)
library(pscl)
library(RColorBrewer)
library(rworldmap)
library(reshape)
library(reshape2)
library(rgeos)
library(rgdal)
library(raster)
library(sp)
library(utils)
library(xtable)
library(dplyr)
## get data
# set wd
# setwd("~/Massey 2014/DHayman_20140627")
# read data
data<-read.csv("DHayman_20140627.csv",header=T)
vac<-read.csv("DHayman_20140715_Vacc.csv",header=T)
names(data)
data$RptYear<-as.factor(data$RptYear)
data$SurvWeek<-as.factor(data$SurvWeek)
data$NZDep01<-as.factor(data$NZDep01)
data$NZDep06<-as.factor(data$NZDep06)
data$NZDep13<-as.factor(data$NZDep13)
#data$AgeInYears<-as.factor(data$AgeInYears)
data$EthnicityPrioritised<-as.factor(data$EthnicityPrioritised)

@@

\begin{table}[htdp]
\begin{center}
<<include=FALSE,echo=FALSE,results=tex>>=
  library(dplyr)
  PopnImmunityAll <- read.csv("data/PopnImmunityAll.csv") %>%
                       mutate(YS=2013-AgeEnd, YE=2013-AgeStart) %>%
                       mutate(YOB=ifelse(YS==YE,YS,ifelse(is.finite(YS), paste(YS,YE,sep="--"), paste0("<", YE)))) %>%
                       select("Year of Birth"=YOB, "Proportion Immune"=Immunity)
  print(xtable(PopnImmunityAll, align=rep("c",3)), include.rownames=F, floating=FALSE)
@
\end{center}
\caption{Vaccination coverage (2006--2013 years) and serosurvey estimates of immunity ($>2006$ years) among different age classes used in these analyses, as provided by the Ministry of Health up to 1st January 2014. Note these values are from vaccination records and serosurveys. Vaccine efficacy for 0--4 year olds was 96\%, 5--13 year olds 99\%, and for $\geq$ 14 year olds equivocal serological results were considered non-immune. Note that 28\% of those $<1$ were considered immune due to passive immunity, following \citep{waaijenborg}.}
\label{table:sero}
\end{table}%

>>>>

<<echo=FALSE,include=FALSE,results=hide>>=
rm(list=ls())

### NOTE: DON'T CHANGE THE ORDER OF THESE INCLUDES
library(MASS)
library(plyr)
library(reshape)
library(raster)
library(dplyr)
###

vacc_dhb <- read.csv("tables/dhb_vacc.csv")
totals   <- vacc_dhb[nrow(vacc_dhb), ,drop=FALSE]
vacc_reqd_percent    <- totals$PC * 100
vacc_reqd_dhb_min    <- min(vacc_dhb$PC) * 100
vacc_reqd_dhb_max    <- max(vacc_dhb$PC) * 100
vacc_reqd_auckland   <- min(floor((vacc_dhb %>% filter(DHB == "Auckland" | DHB == "CountiesManakau" | DHB == "Waitemata") %>% select(Vaccination)) / 1000)) * 1000
vacc_reqd_count      <- totals$Vaccination
naive_percent        <- round(totals$Naïve / totals$Population * 100)
break_even_vacc_cost <- 259 # vaccine costs such that benefits == cost (from .xlsx)
@

@@

<<echo=FALSE,include=FALSE,results=hide>>=
#library(adehabitat)
library(classInt)
library(ggplot2)   # plotting library
library(grid)
library(gridExtra)
library(ggmap)
library(Hmisc)
library(maps)       # Provides functions that let us plot the maps
library(mapdata)    # Contains the hi-resolution points that mark out the countries.
library(maptools)
library(mapproj)
library(pscl)
library(RColorBrewer)
library(rworldmap)
library(reshape2)
library(rgeos)
library(rgdal)
library(sp)
library(utils)
library(xtable)
library(dplyr)
## get data
# set wd
# setwd("~/Massey 2014/DHayman_20140627")
# read data
data<-read.csv("DHayman_20140627.csv",header=T)
vac<-read.csv("DHayman_20140715_Vacc.csv",header=T)
names(data)
data$RptYear<-as.factor(data$RptYear)
data$SurvWeek<-as.factor(data$SurvWeek)
data$NZDep01<-as.factor(data$NZDep01)
data$NZDep06<-as.factor(data$NZDep06)
data$NZDep13<-as.factor(data$NZDep13)
#data$AgeInYears<-as.factor(data$AgeInYears)
data$EthnicityPrioritised<-as.factor(data$EthnicityPrioritised)

@@

\begin{table}[htdp]
\begin{center}
<<include=FALSE,echo=FALSE,results=tex>>=
  PopnImmunityAll <- read.csv("data/PopnImmunityAll.csv") %>%
                       mutate(YS=2013-AgeEnd, YE=2013-AgeStart) %>%
                       mutate(YOB=ifelse(YS==YE,YS,ifelse(is.finite(YS), paste(YS,YE,sep="--"), paste0("<", YE)))) %>%
                       select("Year of Birth"=YOB, "Proportion Immune"=Immunity)
  print(xtable(PopnImmunityAll, align=rep("c",3)), include.rownames=F, floating=FALSE)
@
\end{center}
\caption{Vaccination coverage (2006--2013 years) and serosurvey estimates of immunity ($>2006$ years) among different age classes used in these analyses, as provided by the Ministry of Health up to 1st January 2014. Note these values are from vaccination records and serosurveys. Vaccine efficacy for 0--4 year olds was 96\%, 5--13 year olds 99\%, and for $\geq$ 14 year olds equivocal serological results were considered non-immune. Note that 28\% of those $<1$ were considered immune due to passive immunity, following \citep{waaijenborg}.}
\label{table:sero}
\end{table}%
